Fig3

### 2020-03-29 analysis/figure-3.Rmd
now with better fig 3 and 6

g <- makeboxplots(gonvsd, c( "AVPR1A"), "Female gonads", "female", c( "lay", "inc.d3", "inc.d9"))  +
  labs(caption = " ", x = " ")
h <- makeboxplots(gonvsd, c( "EGR1", "FOS", "PRLR"), " ", "female", c( "lay", "inc.d3"))  +
  theme(axis.title.y = element_blank()) + labs(caption = " ")
f <- makeboxplots(pitvsd, c("LBH", "PRL"), "Male pituitary", "male", 
                  c("inc.d9", "inc.d17")) + 
  theme(plot.caption = element_text(face = "italic")) + 
  labs(x = " ",
       caption = "Candidate genes that were not differentially expressed from bldg to n5: AVP, AVPR1B, ESR2,  GNRH1, JUN, OXT, VIP.")

>>>>

g <- makeboxplots(gonvsd, c( "AVPR1A"), "Female gonads", "female", c( "lay", "inc.d3", "inc.d9"))  +
  labs(caption = " ", x = " ")
h <- makeboxplots(gonvsd, c( "EGR1", "FOS", "PRLR"), " ", "female", c( "lay", "inc.d3"))  +
  theme(axis.title.y = element_blank()) + labs(caption = " ")
f <- makeboxplots(pitvsd, c("LBH", "PRL"), "Male pituitary", "male", 
                  c("inc.d9", "inc.d17")) + 
  theme(plot.caption = element_text(face = "italic")) + 
  theme(axis.title.y = element_blank()) +
  labs(x = " ",
       caption = "Candidate genes that were not differentially expressed from bldg to n5: AVP, AVPR1B, ESR2,  GNRH1, JUN, and OXT.")
